Centralized Programming for Distributed Control Planes

### 2016-01-25 paper/compilation.tex
fixing bug with MEDs on external ASes

\newcommand{\Router}[1]{ \textbf{Router #1:} }
\newcommand{\REGEX}[1]{ \text{regex}(#1) }
\newcommand{\PEER}{ \text{peer} }
\newcommand{\COMM} {\text{comm}}
\newcommand{\MED} {\text{MED}}

\begin{figure}[t!]
\begin{lstlisting}[frame=single, mathescape=true] 
$\Router{A}$
  Match $\PEER=C, \COMM=(3,2)$
    Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
$\Router{B}$
  Match $\PEER = C, \COMM = (-,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$ 
           $\MED \leftarrow 81, \PEER \leftarrow W$
  Match $\PEER = C, \COMM = (3,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$ 
           $\MED \leftarrow 81, \PEER \leftarrow W$
$\Router{C}$
  Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
  Match $\PEER = D, \COMM = (2,2)$
    Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
$\Router{D}$
  Match $\REGEX{X + Y}$
    Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
$\Router{E}$
  Match $\REGEX{Z}$
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
\end{lstlisting}
\label{fig:config}
\caption{Abstract BGP router configurations.}
\end{figure}

>>>>

\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}
\newcommand{\Router}[1]{ \textbf{Router #1:} }
\newcommand{\REGEX}[1]{ \text{regex}(#1) }
\newcommand{\PEER}{ \text{peer} }
\newcommand{\COMM} {\text{comm}}
\newcommand{\MED} {\text{MED}}

\begin{figure}[t!]
\begin{lstlisting}[frame=single, mathescape=true] 
$\Router{A}$
  Match $\PEER=C, \COMM=(3,2)$
    Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
$\Router{B}$
  Match $\PEER = C, \COMM = (-,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$ 
           $\MED \leftarrow 81, \PEER \leftarrow W$
  Match $\PEER = C, \COMM = (3,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$ 
           $\MED \leftarrow 81, \PEER \leftarrow W$
$\Router{C}$-
  Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
  Match $\PEER = D, \COMM = (2,2)$
    Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
$\Router{D}$
  Match $\REGEX{X + Y}$
    Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
$\Router{E}$
  Match $\REGEX{Z}$
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
\end{lstlisting}
\label{fig:config}
\caption{Abstract BGP router configurations.}
\end{figure}
